Estimating the magnetization distribution within rectangular rock samples

### 2016-07-22 manuscript/manuscript.tex
point 3 of reviewer 2

The magnetic sensors used in paleomagnetic applications have
different active area (or volume). 
\citet{uehara2007, uehara2008} presented a magneto-impedance (MI) 
sensor whose cylindrical active volume has $36$ $\mu$m in diameter and 
$5500$ $\mu$m in length, which limits its spatial resolution
if compared with the giant magnetoresistance 
(GMR) sensor presented by \citet{hankard2009} and the magnetic 
tunnel junction (MTJ) sensor presented by \citet{lima2014}, for example.
These two sensors are considered planar and have active areas
of, respectively, $9$~$\mu$m~$\times$~$36$~$\mu$m and 
$\approx 4$~$\mu$m~$\times$~$2$~$\mu$m.
Finally, \citet{fong2005} used a custom-designed low-transition-temperature 
superconducting quantum interference device (low T$_{c}$ SQUID) sensor
which is also considered planar and has an active area with
effective diameter of $80$~$\mu$m.
This is currently one of the most powerful magnetic sensors.

>>>>

The magnetic sensors used in paleomagnetic applications have
different active area (or volume). 
\citet{uehara2007, uehara2008} presented a magneto-impedance (MI) 
sensor whose cylindrical active volume has $36$ $\mu$m in diameter and 
$5500$ $\mu$m in length, which limits its spatial resolution
if compared with the giant magnetoresistance 
(GMR) sensor presented by \citet{hankard2009} and the magnetic 
tunnel junction (MTJ) sensor presented by \citet{lima2014}, for example.
These two sensors are considered planar and have active areas
of, respectively, $9$~$\mu$m~$\times$~$36$~$\mu$m and 
$\approx 4$~$\mu$m~$\times$~$2$~$\mu$m.
Finally, \citet{fong2005} used a bare SQUID design with an 
active diameter of $120$~$\mu$m. In this case, the sensor 
is also considered planar.
